### 2020-10-25 thesis/msc-thesis.tex
codespaces

\documentclass[
     12pt,         % font size
     a4paper,      % paper format
     BCOR10mm,     % binding correction
     DIV14,        % stripe size for margin calculation
%     liststotoc,   % table listing in toc
%     bibtotoc,     % bibliography in toc
%     idxtotoc,     % index in toc
%     parskip       % paragraph skip instad of paragraph indent
     ]{scrreprt}

@@

\subsection{Training Promotion (BAfï¿½G)}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

@@

\subsection{e-Prescription}
Reference can be found in the "Ärzteblatt" \cite{Ärzteblatt}.
\\\\
The user can have the right to manage his prescriptions via an App. Doctors give digital prescriptions to users app,
which can digitally be used in pharmacies also without physically being there.
\\\\
Regulation: "Gesetz für mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
\\\\
e-Prescription processes \cite{gematik-e-rezept}
\begin{enumerate}
     \item Doctor creates digital prescription if he has access to "Telematikinfrastruktur" and "Heilberufausweis"
     \item Prescription is saved on "Telematikinfrastruktur"
     \item Doctor displays a QR-Code (prescription-token)
     \item Patient can receive QR-Code in App (or get a printout)
     \item Patient can check availability of drug in pharmacies via the app
     \item Patient can "apply" the prescription to a pharmacy via the app
     \item prescription is now irrevocably bound to the pharmacy and gets reserved
     \item pharmacy can use prescription-token (in QR-Code) to access prescription in "Telematikinfrastruktur"
     \item pharmacy notifies patient if or when the drug is available
     \item drug can be picked up by patient or be delivered
     \item If user picks drug up, he can show QR-Code in app or on printout (he got from doctor)
     \item pharmacy can access "Telematikinfrastruktur" to validate prescription
     \item pharmacy gives drug if validated
\end{enumerate}
~\\
Enterprises are "allowed" to provide the IT-Structure behind the App, meaning the communication with a pharmacy and the receiving of prescription-tokens.
\\\\
What are services and what are self-services in this scenario:
\begin{itemize}
     \item Service: Access to prescription. Self-service: Digital management of prescriptions (prescription-tokens) inside app
     \item Service: Receiving drug for valid prescription. Self-service: Digital delivery of prescription (prescription-token)
           to pharmacy and digital instruction of delivery of drug
\end{itemize}

>>>>

\documentclass[
     12pt,         % font size
     a4paper,      % paper format
     BCOR10mm,     % binding correction
     DIV14,        % stripe size for margin calculation
%     liststotoc,   % table listing in toc
%     bibtotoc,     % bibliography in toc
%     idxtotoc,     % index in toc
%     parskip       % p
aragraph skip instad of paragraph indent
     ]{scrreprt}

@@

\subsection{Training Promotion (BAföG)}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

@@

\subsection{e-Prescription}
Reference can be found in the "rzteblatt" \cite{Ärzteblatt}.
\\\\
The user can have the right to manage his prescriptions via an App. Doctors give digital prescriptions to users app,
which can digitally be used in pharmacies also without physically being there.
\\\\
Regulation: "Gesetz fï¿½r mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
\\\\
e-Prescription processes \cite{gematik-e-rezept}
\begin{enumerate}
     \item Doctor creates digital prescription if he has access to "Telematikinfrastruktur" and "Heilberufausweis"
     \item Prescription is saved on "Telematikinfrastruktur"
     \item Doctor displays a QR-Code (prescription-token)
     \item Patient can receive QR-Code in App (or get a printout)
     \item Patient can check availability of drug in pharmacies via the app
     \item Patient can "apply" the prescription to a pharmacy via the app
     \item prescription is now irrevocably bound to the pharmacy and gets reserved
     \item pharmacy can use prescription-token (in QR-Code) to access prescription in "Telematikinfrastruktur"
     \item pharmacy notifies patient if or when the drug is available
     \item drug can be picked up by patient or be delivered
     \item If user picks drug up, he can show QR-Code in app or on printout (he got from doctor)
     \item pharmacy can access "Telematikinfrastruktur" to validate prescription
     \item pharmacy gives drug if validated
\end{enumerate}
~\\
Enterprises are "allowed" to provide the IT-Structure behind the App, meaning the communication with a pharmacy and the receiving of prescription-tokens.
\\\\
What are services and what are self-services in this scenario:
\begin{itemize}
     \item Service: Access to prescription. Self-service: Digital management of prescriptions (prescription-tokens) inside app
     \item Service: Receiving drug for valid prescription. Self-service: Digital delivery of prescription (prescription-token)
           to pharmacy and digital instruction of delivery of drug
\end{itemize}
